Trends in Mortality Rates

### 2024-09-27 paper/paper.qmd
Updated and cite R function used

library(tidyverse)
library(ggplot2)
library(dplyr)

@@

The data used in this paper is access in from Open Data Toronto and the particular data set used was the Deaths of Shelter Residents (@toronto_deaths_shelter_residents). To analysis the data and creating graphs using the data, following package that was build in the (R program @citeR) was used: tidyverse (@tidyverse), dplyr (@dplyr), knitr (@knitr), and ggplot2 (@ggplot2). LLM (@openai2023chatgpt) was also use for this paper in term of helping with coding in R to graph data, simulating a data, cleaning data, and revising writing.

@@

library(knitr)
library(dplyr)

@@

library(ggplot2)
library(tidyr)
library(dplyr)

@@

# Load necessary libraries
library(ggplot2)
library(dplyr)
library(gridExtra)

>>>>

library(tidyverse)
library(ggplot2)
library(dplyr)
library(knitr)
library(tidyr)
library(gridExtra)

@@

The data used in this paper is access in from Open Data Toronto and the particular data set used was the Deaths of Shelter Residents (@toronto_deaths_shelter_residents). To analysis the data and creating graphs using the data, following package that was build in the (R program @citeR) was used: tidyverse (@tidyverse), dplyr (@dplyr), tidyr (@tidyr), gridExtra (@gridExtra), knitr (@knitr), and ggplot2 (@ggplot2). LLM (@openai2023chatgpt) was also use for this paper in term of helping with coding in R to graph data, simulating a data, cleaning data, and revising writing.

@@

@@

@@
